Bow shocks, bow waves, and dust waves

### 2018-08-23 papers/Papers1234/sec-dust-case-studies.tex
Add some details of LP Ori to the Case Studies section
But I have now broken out this work into a new repo

https://github.com/div-B-equals-0/dust-wave-case-studies
Start writing up the magnetic field part for dust wave paper
Write a bit more about the B fields
Return to the observations section

\section{Case studies}
\label{sec:case-studies}

Carina mid-infrared bow shocks \citep{Sexton:2015b} are in a high
density environment, \SI{1000}{cm^{-3}}, so they may be bow waves.
There seems to be spectral types for most of them: B0 (but supergiant)
to O7.  Sizes are 3 to 12 arcsec, which at Carina (\SI{2.3}{kpc}) is
\SIrange{0.033}{0.134}{pc}.

@@

>>>>

\section{Observational evidence for radiation-supported bows}
\label{sec:case-studies}

In observational studies of bow-shaped arcs around OB stars, it is
frequently assumed that all such objects are wind-supported bow shocks
(e.g., \citealp{Kobulnicky:2016a}). Our results from
\S~\ref{sec:strong-gas-grain} show that this is indeed a fair
assumption in the absence of gas-grain decoupling, so long as the
ambient density is less than about \SI{100}{cm^{-3}} (see
Fig.~\ref{fig:zones-v-n-plane}). In other words, most OB stars
interacting with the diffuse interstellar medium are probably in the
wind bow shock regime.  Therefore, to find examples of
radiation-supported bow waves and bow shocks it is necessary to look
at arcs inside \hii{} regions and star-forming clouds, where the
ambient densities are much higher.

One potentially promising sample is the Carina mid-infrared bow shocks
\citep{Sexton:2015b}.   are in a high density environment,
\SI{1000}{cm^{-3}}, so they may be bow waves.  There seems to be
spectral types for most of them: B0 (but supergiant) to O7.  Sizes are
3 to 12 arcsec, which at Carina (\SI{2.3}{kpc}) is
\SIrange{0.033}{0.134}{pc}.

@@

Two small bows in M42:

\(\theta^1\)\,Ori~D (Ney--Allen nebula) \citep{Robberto:2005a}

LP~Ori: B1.5V star, like our \SI{10}{M_\odot} example. Radius about
\(3''\), so 0.005 pc.  With \(v = 80\) that would clearly be a dust
wave and would require \SIrange{100}{1000}{cm^{-3}}. Gaia distance \SI{408 +- 11}{pc}

Ones that Ochsendorf claims are dust waves (Narrator: they aren't).
